---
editor_options:
  chunk_output_type: console
output:
  pdf_document: default
  word_document: default
---

\newpage

# Supplementary 1 {-}

Due to the high number of missing working impressions, we conducted a sensitivity analysis including data that was matched without working impression as a variable. Figure \@ref(fig:fig6-no-wi) shows the change in proportion of appropriate non-conveyance in this group. The results of the segmented regression can be seen in Table \@ref(tab:cits-table-no-wi) and demonstrate a smaller increase appropriate non-conveyance in the intervention group relative to the control group of `r cits_tidy_no_wi$estimate[7]`% (95%CI `r cits_tidy_no_wi$ci[7]`%, p`r cits_tidy_no_wi$p.value[7]`), but smaller decrease in the trend of appropriate non-conveyance (`r cits_tidy_no_wi$estimate[8]`%, 95%CI `r cits_tidy_no_wi$ci[8]`%, p=`r cits_tidy_no_wi$p.value[8]`).

```{r fig6-no-wi, fig.cap="Effect of 10-week primary care rotation on appropriate non-conveyance (excluding working impression). a) Monthly appropriate non-conveyance rates b) Fitted CITS model. Dashed lines represent the counterfactuals.", fig.height = 10}

#source('Code/prep_no_wi.R')

ggpubr::ggarrange(fig5_no_wi, fig6_no_wi, nrow = 2, ncol = 1, labels = "auto", common.legend = T)

```

```{r cits-table-no-wi, cache = F}
knitr::kable(ols_table_no_wi, caption="Result of segmented regression analysis for appropriate non-conveyance (excluding working impression)", booktabs = TRUE, longtable = T, format = format) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), latex_options = c("repeat_header", "striped", "hold_position")) %>%
  column_spec(1, width = "25em")
```

\newpage


# Supplementary 2 {-}

The following figures highlight the difference in triage call acuity (Figure \@ref(fig:fig3)) and NEWS risk category (Figure \@ref(fig:fig4)) pre- and post-placement, demonstrating the need for a control in the study design.



```{r fig3, fig.cap="Call category pre- and post-placement"}

df1a <- df %>%
  select(newTimeElapsed, call_cat, risk, intervention)

levels(df1a$call_cat) <- c("category 1", "category 2", "category 3", "category 4", "category 5")

df1a <- df1a %>%
  mutate(
    call_cat = case_when(
      call_cat == "cat1" ~ "category 1",
      call_cat == "cat2" ~ "category 2",
      call_cat == "cat3" ~ "category 3",
      call_cat == "cat4" ~ "category 4",
      TRUE ~ "category 5"
    )
  )


ggplot(df1a, aes(x = newTimeElapsed, fill = call_cat)) +
  geom_histogram(binwidth =1, position="fill", color="black", size = 0.1) +
  scale_x_continuous(name="Months elapsed", breaks = seq(1,24,1), labels = seq(1,24,1), expand = c(0,0)) +
  scale_y_continuous(name = "Percentage of incidents", expand = c(0,0), breaks=seq(0,1,0.1), limits = c(0,1), labels=scales::percent) +
  labs(fill="Call Category") + 
  theme(legend.position = "bottom", axis.title.x = element_text(vjust = -1)) + 
  geom_vline(xintercept = 12.5, size = 1.5) +
  scale_fill_viridis_d() +
  annotate("label", label = "Pre-placement", x = 4, y = 0.9, size = 4, colour = "black") +
  annotate("label", label = "Post-placement", x = 16, y = 0.9, size = 4, colour = "black")

```

```{r fig4, fig.cap="NEWS category pre- and post-placement", fig.pos="p"}

ggplot(df, aes(x = newTimeElapsed, fill = risk)) +
  geom_histogram(binwidth =1, position="fill", color="black", size = 0.1) +
  scale_x_continuous(name="Months elapsed", breaks = seq(1,24,1), labels = seq(1,24,1), expand = c(0,0)) +
  scale_y_continuous(name = "Percentage of incidents", expand = c(0,0), breaks=seq(0,1,0.1), limits = c(0,1), labels=scales::percent) +
  scale_fill_brewer("NEWS risk category") +
  theme(legend.position = "bottom", axis.title.x = element_text(vjust = -1)) + 
  geom_vline(xintercept = 12.5, size = 2) +
  annotate("label", label = "Pre-placement", x = 4, y = 0.9, size = 4, colour = "black") +
  annotate("label", label = "Post-placement", x = 16, y = 0.9, size = 4, colour = "black")

```


\newpage
